Towards semantic-rich word embeddings

### 2019-03-26 paper/main.tex
Add appendix with confusion matrices

%% Useful packages
%\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{array}
\usepackage{tcolorbox}

@@

>>>>

%% Useful packages
%\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{array}
\usepackage{tcolorbox}
\usepackage[toc,page]{appendix}

@@

\newpage
\appendix
\section{Appendix}
\label{sec:appendix}

Fig. \ref{fig:cm_tree}-\ref{fig:cm_pool} depict confusion matrices for meanings of ambiguous words, displaying how frequently each keyword was confused with others, before (\ref{sec:baseline_model})(left matrices) and after optimization (\ref{sec:optimization})(right matrices).
Each confusion matrix was limited to meanings of one ambiguous word, with other keywords labeled as \textit{other} on the graph.

Model with context length \(l=4\) was used.  Optimization was done for 4 epochs with \(\alpha=0.15, \beta=0.04\) on the train set. Both baseline and optimized model were evaluated on the test set of 10 usage examples per keyword (\ref{sec:dataset}).

\begin{figure}
    \centering
    \caption{Confusion matrices for \textit{tree} keywords.}
    \label{fig:cm_tree}
    \includegraphics[scale=0.38]{res/cm_tree.png}
\end{figure}

\begin{figure}
    \centering
    \caption{Confusion matrices for \textit{nail} keywords.}
    \label{fig:cm_nail}
    \includegraphics[scale=0.38]{res/cm_nail.png}
\end{figure}

\begin{figure}
    \centering
    \caption{Confusion matrices for \textit{mars} keywords.}
    \label{fig:cm_mars}
    \includegraphics[scale=0.38]{res/cm_mars.png}
\end{figure}

\begin{figure}
    \centering
    \caption{Confusion matrices for \textit{bolt} keywords.}
    \label{fig:cm_bolt}
    \includegraphics[scale=0.38]{res/cm_bolt.png}
\end{figure}

\begin{figure}
    \centering
    \caption{Confusion matrices for \textit{season} keywords.}
    \label{fig:cm_season}
    \includegraphics[scale=0.38]{res/cm_season.png}
\end{figure}

\begin{figure}
    \centering
    \caption{Confusion matrices for \textit{pool} keywords.}
    \label{fig:cm_pool}
    \includegraphics[scale=0.38]{res/cm_pool.png}
\end{figure}
